MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-04-29 Article.tex
Fixed url of MaBoSS repo

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}, \url{https://github.com/sysbio-curie/MaBoSS-env-2.0}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/sysbio-curie/hpcmaboss-artifact}}.

>>>>

The source code of the proposed implementations is publicly available at their respective GitHub repositories\footnote{\url{https://github.com/sysbio-curie/MaBoSS.GPU}, \url{https://github.com/sysbio-curie/MaBoSS}}. We also provide the scripts, presented plots, data and instructions to reproduce the benchmarks in the replication package\footnote{\url{https://github.com/sysbio-curie/hpcmaboss-artifact}}.
